Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-03 paper.tex
intro to reproducibility

        This chapter will examine how different workflow engines tackle the 
        issue of reproducibility. Section~\ref{prov} will discuss how the 
        engines assimilate and distribute the provenance data. 
        Section~\ref{repcont} will examine how these engines use containers to
        facilitate reproducibility of the experiments.
        \section{Provenance Tracking}\label{prov}

>>>>

        This chapter will examine how different workflow engines tackle the 
        issue of reproducibility. Section~\ref{prov} will discuss how the 
        engines assimilate and distribute the provenance data. 
        Section~\ref{repcont} will examine how these engines use containers to
        facilitate reproducibility of the experiments.
        \section{Provenance Tracking}\label{prov}
            Provenance tracking is of vital importance to scientific reporting.
            On its own, source code is insuffient to reproduce the workflow 
            described in a research paper. This is because source code does 
            not specify the specific dataset used nor the specific versions of
            tools and the environments that they were executed on. Minor 
            changes to any of these features can significantly affect results.

            As explained by the W3 PROW specification, provenance details 
            information on the data, the tools involved in its creation and the
            responsible parties. Provenance tracking, in the context of 
            workflows, is the the act of capturing provenance data during
            workflow execution. With detailed provenance and access to source 
            codeinfo, researchers should have enough information to be able 
            to reproduce workflows.

            To to the importance of provenance tracking for scientific 
            workflows several workflow engines adapted strategies to capture 
            comprehensive provenance data. These include Nipype, PSOM, FastR, 
            LONI, Taverna, Pegasus, Nextflow, Galaxy. Other workflow engines,
            such as SPM, AA, Pydpiper,
